Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2020-07-21 manuscript/main.tex
Explicitly reference CDC's FluSight network for short-term forecasts

Finally, we observed that composite models of multiple orthogonal fitness metrics often outperformed models based on their individual components.
These results are consistent with previous work that found improved performance by integrating components of antigenic drift, functional constraint, and clade growth \cite{Luksza:2014hj}.
However, the effective elimination of LBI from our three-metric model during the validation period (Fig.~\ref{fig:unadjusted_composite_model_accuracy_and_coefficients_for_natural_populations}) reveals the limitations of our current additive approach to composite models.
The recent success of weighted ensembles for short-term influenza forecasting \cite{Reich:2019bq} suggests that long-term forecasting may benefit from a similar approach.

>>>>

Finally, we observed that composite models of multiple orthogonal fitness metrics often outperformed models based on their individual components.
These results are consistent with previous work that found improved performance by integrating components of antigenic drift, functional constraint, and clade growth \cite{Luksza:2014hj}.
However, the effective elimination of LBI from our three-metric model during the validation period (Fig.~\ref{fig:unadjusted_composite_model_accuracy_and_coefficients_for_natural_populations}) reveals the limitations of our current additive approach to composite models.
The recent success of weighted ensembles for short-term influenza forecasting through the CDC's FluSight network \cite{Reich:2019bq} suggests that long-term forecasting may benefit from a similar approach.
